\subsection*{Conclusion}
\subsubsection*{Part 1}
Adaptive cruise control is a system that is easily written as a hybrid automaton as it required only 3 modes and one discrete state to describe the dynamics of the system as described in Step 1.1. The size of the hybrid automaton of a ACC depends on the level of complexity of the ACC and as the ACC described in Step 1.1 was rather simple, the size of the hybrid automaton was kept to a minimum.   

% There are probably many different ways of creating a hybrid automaton of a Adaptive cruise control system,

% It could even be reduced to two nodes if the normal operation mode is left out and you start at $q_2$ and ...

\subsubsection*{Part 2}
Since we failed to simulate and compute the optimal control input, it is difficult to draw a conclusion about the performance of the MPC controller of this hybrid system. We have seen the potential of Model Predictive controllers in other situations, and we suspect that it is very much suited for hybrid systems, since MPC can deal with constraints, where most other control strategies cannot. Since the sampling time of this grid system is rather low, the MPC should not run into time issues due to computational complexity. Step 2.10 should show how very specific constraints, like a constraint on a single time step, can be incorporated into MPC. We cannot think of any other control method that allows for these kind of constraints/objectives.

\subsection*{Evaluation}
\subsubsection*{Part 1}
There are probably many different ways of creating a hybrid automaton of a Adaptive cruise control system, we managed to create one with 3 modes and one discrete state for turning the ACC on/off. This can probably be reduced even further by removing the normal operation mode ($q_1$) of the car and only describing the ACC part. But keeping mode $q_1$ creates a handy loop in which the system can switch between the driver taking control and the ACC controlling the car. The guard condition $G(q_1,q_2)$ depended on the distance between the two cars, which was not a state in the state description of mode $q_1$. This raised some questions whether it should be added to the state description of that mode or be viewed as a outside interrupt from the sensor. the latter has been chosen as the dynamics in that mode didn't depend on that state.\\
\\
Part 1 showed that any kind of dynamic can be modeled by a hybrid automaton, although the size and complexity can grow rapidly with more complex dynamics.

\subsubsection*{Part 2}
This assignment gave us the insight in how to model event-based models. Part 2 of the assignment learned us how to cast a, for us more intuitive, piecewise affine model into a MLD model. It became clear that the MLD model is very well suited for MPC. The recasting of model is a tedious task that requires accuracy and precision. Representing the MLD model in vector-matrix form was new for us. After vectoring the matrices, we noticed that there were more unknown variables than $u$, $\delta$ and $z$, so we had to alter the $M_i$ and $F_i$ matrices. If a similar problem arises now, we would first consider what all the unknown variables are, before we start vectorising.\\
\\
Furthermore, we were unable to find our mistake. We should have had more care in ensuring our answers were correct. After the simulation failed, it was too late to find the mistake. Since there was a large amount of constraints and unknowns, it is very difficult to inspect the matrices and see if they are correct.\\
\\
Additionally, it became apparent how easy it is to approximate a nonlinear function with a piecewise affine function. Connecting the boundaries was also trivial, since it came down to adding some equality constraints. The plots showed some good approximations, better than we expected.\\
\\
The most important thing learned for this assignment, is how many constraints there are for a relatively concise model of only three parts. A large part of the constraints are the result of the PWA function $\hat{f}$. Representing the MLD model with less decision and auxiliary variables would reduce the number of constraints, and thus the risk of a mistake. Taking the effort to use the most concise MLD model might take more time in creating the MLD model, but it is probably worth it, since it takes effort away later.\\
\\
Overall, this assignment is our first introduction with hybrid systems. It showed us available modeling structures, capable of capturing the switching dynamics. We understand the reason to write a model in MLD structure, since this structure can be recast into an optimisation problem. The PWA or hybrid automaton model could not directly be used for MPC. These types of assignments force you to delve deeper into the material than lectures and a written exam ever could.\\
\\
All the code can be found in \cite{GIT}, and in the appendices.